\begin{center} \bf \sffamily \LARGE Prisoner's dilemma with stochastic payoffs\\[-1cm] \end{center}

### 2021-11-24 main.tex
fixing errors

%% Adding shortcut commands to refer to our figures %%
\newcommand{\FigEvoProc}{{\bf Fig.~1}}
\newcommand{\FigInvAnalysis}{{\bf Fig.~2}}
\newcommand{\FigResultsOverPara}{{\bf Fig.~3}}

@@

\tikzset{
  treenode/.style = {align=center, inner sep=0pt, text centered,
    font=\sffamily},
  arn_n/.style = {treenode, circle, white, font=\sffamily\bfseries, draw=black, inner sep=-6pt,
    fill=black, text width=1.5em},% arbre rouge noir, noeud noir
  arn_r/.style = {treenode, circle, red, 
    text width=1.5em, very thick, inner sep=4pt},% arbre rouge noir, noeud rouge
  arn_x/.style = {treenode, rectangle, draw=black,
    minimum width=0.5em, minimum height=0.5em}% arbre rouge noir, nil
}

@@

\title{
\bf  \sffamily \LARGE Evolution of cooperation among individuals with limited payoff memory\\}
\date{}
\author{Nikoleta E. Glynatsi, Christian Hilbe, Alex McAvoy}

@@

\begin{abstract}
Repeated games are vastly used in evolutionary ame theory to explain cooperation in a variety of environments. Although existing models have shaped our understanding of human cooperation, they often work with idealized
assumptions. In an evolutionary process, individuals aimitate other individuals
of the population based on their fitness. It is commonly assumed that an
individual computes their fitness after interacting with a representative sample
of the population, and remembering all the interactions they participated in. In
real life, we do not always remember all our interactions, instead we rather
recall our most recent ones.

Here, we introduce a framework that allows individuals to estimate their fitness
based on a minimum of social information. We explore the difference between our
framework and the classical framework using computer simulations. We present results for
the most commonly used classes of symmetric \(2 \times 2\) games. The
simulations show that, in the prisoner's dilemma individuals with limited memory
tend to adopt less generous strategies and they achieve less cooperation than in
the classical scenario. In contrast, in the stag-hunt and the harmony game, the
impact of memory is less striking. Here individuals with limited memory perform
nearly as well as individuals with full memory. Finally, we observe that the
snowdrift game is the only game for which cooperation can be underestimated in
the classical scenario.
\end{abstract}

@@

One of the most important applications of evolutionary game theory is the
evolution of cooperation. Why is it that some individuals choose to help others,
increasing their payoff, at the expense of decreasing one's own? In evolutionary
game theory individuals are not required to be rational, instead they adapt
strategies based on mutation and exploration. Strategies are more likely to
spread if they have a high fitness either because the individuals who adopt them
have more offspring, or because they are imitated more often~\cite{Wu2015}. The
fitness of a strategy is not constant but depends on the composition of the
population. Individuals interact based on their strategies with other members of
the population and the payoffs they yield are translated into fitness.

It is commonly assumed that individuals compute their fitness after interacting
with a representative sample of the population, and remembering all the
interactions they participated in~\cite{Nowak2006, nowak2004emergence,
Hilbe2013, Hilbe2018,Reiter2018, garcia2018no, Nowak1992tit, Baek2016}. This
implies that individuals have a perfect memory. However, when modelling how
individuals make decisions in each turn they are assumed to have very limited
memory. To be precise, most of the studies in the literature focus on naive
subjects who can only choose from a restricted set of
strategies~\cite{Nowak1992tit}, or who do not remember anything beyond the
outcome of the very last round~\cite{Baek2016}. Note that there are a few
notable exceptions~\cite{Hauert1997, Stewart2016}.

Studies that make use of this classical framework report that cooperation can
substantially evolve. However, the inconsistency in the memory size of players
leads us to question the robustness of our understanding of cooperation. To this end, we
propose a framework in which individuals, similar to the decisions at each turn,
estimate their fitness based on a minimum of information. Though we are not the
first to question the assumptions of estimating fitness~\cite{Roca2006}, we are
the first to explore the effect of memory.

@@

# This needs an intro, guiding readers into the model.

Just words.

@@

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.70\textwidth]{static/expected_and_stochastic_for_donation_game.pdf}\vspace{-3cm}
    \includegraphics[width=.70\textwidth]{static/expected_and_stochastic_for_donation_game_b_10.pdf}
    \caption{{\bf Evolutionary dynamics under expected payoffs and last round with one interaction payoffs.} 
    We have run two simulations of the evolutionary process described in
    section~\ref{section:model} for $t\!=\!10^7$ time steps. For each time step,
    we have recorded the current resident population ($y,p,q$). Since simulations
    are run for a relatively high continuation probability of $\delta\!=\!0.999$, we
    do not report the players' initial cooperation probability $y$. The graphs show
    how often the resident population chooses each combination ($p,q$) of
    conditional cooperation probabilities in the subsequent rounds. ({\bf A}) If
    players update based on their expected payoffs, the resident population
    typically applies a strategy for which $p\!\approx\!1$ and
    $q\!\le\!1\!-\!c/b\!=\!0.9$. ({\bf B})
    When players update their strategies based on their realized payoffs in the last
    round, there are two different predominant behaviors. The resident population
    either consists of defectors (with $p\!\approx\!q\!\approx\!0$) or of
    conditional cooperators. In the latter case, the maximum level of $q$ consistent
    with stable cooperation is somewhat smaller compared to the expected-payoff
    setting, $q\!<\!0.5$. The cooperation rate within the resident population
    (averaged over all games and over all time steps) is close to 100\%. Parameters:
    $N\!=\!100$, $c\!=\!1$, $\beta\!=\!1$, $\delta\!=\!0.999$.}
    \label{fig:expected_and_stochastic_for_donation}
\end{figure}

@@

\subsection{Effect of updating payoffs in different social dilemmas}\label{section:2_by_2_games}

In the previous section we gained insights into the effects of the updating
payoffs, and into how parameters such as the benefit and the strength of
selection can intensify them. We investigated these effects by using the
donation game. In order to broaden our understanding of the updating payoffs on
different forms of possible human interactions we extend our approach to all
\(2 \times 2\) symmetric games. More specifically, we apply our analysis to four
different classes of games; the harmony, the snowdrift, the prisoner's dilemma
and the stag-hunt games.

We compare the results of the evolutionary process when the updating payoffs are based on the expected
payoffs, and on the last round payoffs for all the four possible classes of
games (Figures~\ref{fig:expected_two_by_two}
and~\ref{fig:last_round_two_by_two}). In Figure~\ref{fig:expected_two_by_two}
each sub figure represents a run of evolutionary process for a different set of
values for \(\mathcal{U}\). Without loss of generality we set \(R=1\) and
\(P=0\)~\cite{Martinez2012, Roca2009}, and we vary the values of the temptation
payoff \(T\) (across the \(x\)-axis) and of the sucker's payoff \(S\) (across
the \(y\)-axis). Starting at the upper left corner and proceeding clockwise the
quadrants correspond to the harmony, the snowdrift, the prisoner's dilemma and
the stag-hunt games.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/expected_two_by_two_games.pdf}
  \caption{{\bf Evolutionary dynamics under expected payoffs for various social dilemmas.}
  We vary the temptation payoff \(T \in \{0.2, 0.6, 1, 1.4, 1.8, 2.2\}\) across
  the \(x\) axis, and  \(S \in \{1.2, 0.8, 0.4, 0, -0.4, -0.8\}\) across the
  \(y\) axis. ({\bf A}) The top left quadrant where \(S > 0\) and \(T \leq 1\)
  corresponds to the harmony game. The preference ordering for the harmony game
  is \(R > T > S > P\). ({\bf B}) The top right quadrant where \(S > 0\) and \(T > 1\)
  corresponds to the snowdrift game. The preference ordering for the snowdrift game
  is \(T > R > S > P\). ({\bf C}) The bottom left quadrant where \(S < 0\) and \(T \leq 1\)
  corresponds to the stag-hunt game. The preference ordering for the stag-hunt game
  is \(R > T > P > S\). ({\bf D}) The bottom right quadrant where \(S < 0\) and \(T > 1\)
  corresponds to the prisoner's dilemma game. The preference ordering for the prisoner's dilemma game
  is \(T > R > P > S\).
  Unless explicitly varied, the parameters of the simulation
  are $N\!=\!100$, $\beta\!=\!10$, $\delta\!=\!0.99$, $t\!=\!5\times 10^7$.}
  \label{fig:expected_two_by_two}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=\textwidth]{static/stochastic_two_by_two_games.pdf}
  \caption{{\bf Evolutionary dynamics under last round payoffs for various social dilemmas.} 
  We vary the temptation payoff \(T \in \{0.2, 0.6, 1, 1.4, 1.8, 2.2\}\) across
  the \(x\) axis, and  \(S \in \{1.2, 0.8, 0.4, 0, -0.4, -0.8\}\) across the
  \(y\) axis. ({\bf A}) The top left quadrant where \(S > 0\) and \(T \leq 1\)
  corresponds to the harmony game. The preference ordering for the harmony game
  is \(R > T > S > P\). ({\bf B}) The top right quadrant where \(S > 0\) and \(T > 1\)
  corresponds to the snowdrift game. The preference ordering for the snowdrift game
  is \(T > R > S > P\). ({\bf C}) The bottom left quadrant where \(S < 0\) and \(T \leq 1\)
  corresponds to the stag-hunt game. The preference ordering for the stag-hunt game
  is \(R > T > P > S\). ({\bf D}) The bottom right quadrant where \(S < 0\) and \(T > 1\)
  corresponds to the prisoner's dilemma game. The preference ordering for the prisoner's dilemma game
  is \(T > R > P > S\).
  Unless explicitly varied, the parameters of the simulation
  are $N\!=\!100$, $\beta\!=\!10$, $\delta\!=\!0.99$, $t\!=\!5\times 10^7$.}
  \label{fig:last_round_two_by_two}
\end{figure}

The harmony game describes an interaction without conflict. In the harmony game
it is in the best interest for both players to cooperate, and in an evolutionary
process cooperators prevail. We observe that for most harmony game runs the
resident population overwhelmingly applies a strategy for which \(p\) and \(q\)
are \(\approx 1\) (Figure~\ref{fig:expected_two_by_two}). The snowdrift game
describes a situation similar to that of the prisoner's dilemma; cooperation
results in a benefit to the opposing player but entailing a cost to the
cooperator. However, in the snowdrift game individuals obtain immediate direct
benefits from the cooperative acts which leads to \(S > P\). In the snowdrift
game more cooperation emerges compared to the prisoner's dilemma. Defection is
never a resident strategy and for the same values of temptation the overall
\(q-\) values are higher. The last class of games we present are for the stag-hunt
game. In the stag-hunt game there is an equilibrium in which both players
cooperate as well as one in which both defect. For small values of the
temptation and the sucker's payoffs we observe that cooperation prevails similar
to the harmony game. However, in the case where the temptation and the reward
payoffs are equal the resident population either consists of defectors or
cooperators.

Although the patterns of the evolved populations remain similar if we consider
that players update their strategies based on their last round payoff
(Figure~\ref{fig:last_round_two_by_two}), there are still dissimilarities
between the two approaches. To better understand these dissimilarities, we
explore the cooperation rates for each of the cases of the social dilemmas we
have presented (Figure~\ref{fig:cooperation_rates_two_by_two_part_one}).

In the harmony game the cooperation rates for both approaches are similar. The
biggest difference occurs for \(T=1\), nevertheless, it is less than 10\%. There
are two instances for which the cooperation rates are higher for the limited
memory payoffs compared to the expected. These are for \(T=2.2, S=0.4\) and for
\(T=2.2, S=0.8\). It is only in the snowdrift game that cooperation is
overestimated when a minimum of information is considered. Players are slightly
more likely to cooperate after a cooperation and to forgive after being at the
receiving end of a defection. For the rest of the cases the classical scenario
overestimates the average cooperation rate, supporting the results of the
previous section. There is a substantial difference in the cooperation rates
for the prisoner's dilemma class. We observe that for \(S<-0.4\) cooperation
almost never emerges if players imitate based only on the last round payoff.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=.4\textwidth]{static/expected_two_by_two_games_cooperation.pdf}
  \includegraphics[width=.4\textwidth]{static/stochastic_two_by_two_games_cooperation.pdf}
  \caption{\textbf{Cooperation rates for various social dilemmas.} ({\bf A}) If
  players update based on their expected payoffs. ({\bf B}) If
  players update based on their last round payoffs. We vary the temptation
  payoff \(T \in \{0.2, 0.6, 1, 1.4, 1.8, 2.2\}\)
  across the \(x\) axis, and \(S \in \{1.2, 0.8, 0.4, 0, -0.4, -0.8\}\)
  across the \(y\) axis. Unless explicitly varied, the parameters of the simulation
  are $N\!=\!100$, $\beta\!=\!10$, $\delta\!=\!0.99$, $t\!=\!5\times 10^7$.}\label{fig:cooperation_rates_two_by_two_part_one}
\end{figure}

So far we have explored the difference between the expected payoffs and the last
round payoffs. In order to explore further the effect of limited memory we allow
individuals to remember more. More precisely, up to two interactions and up to
the last two rounds. In total we present results for three more updating
payoffs. These are the payoffs when individuals consider the last two rounds
with another member of the population, the last round with two members of the
population, and the last two rounds with two members of the population.
Similar to the last round payoff, we use simulations and record which strategies
the players adopt over time based
(Appendix~\ref{appendix:further_simulation_results}) and we compare the
evolving cooperation rates to those of the expected payoffs
(Figure~\ref{fig:cooperation_rates_two_by_two_part_two}).

In the case of the last two rounds payoff we make two observations. Initially,
for the harmony, the stag-hunt and the prisoner's dilemma classes the average
cooperation rates are higher than the previous case of the last round payoff.
The rates remain strictly less than in the expected payoffs, however, in the
case of the prisoner's dilemma we observe a significant increase. Secondly, for
the snowdrift class there are more instances for which the cooperation rates are
higher than in the expected payoffs. This could indicate that in the case of the
snowdrift game the expected payoffs underestimate cooperation.
Once players interact with two other members of the population, instead of one,
the expected payoffs strictly yield a higher cooperation rate  even in the case
of the snowdrift game. Similar to the previous result, the difference between
the two approaches is always higher for the prisoner's dilemma class.

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=.33\textwidth]{static/rounds_two_by_two_games_cooperation.pdf}
  \includegraphics[width=.33\textwidth]{static/opponents_two_by_two_games_cooperation.pdf}
  \includegraphics[width=.33\textwidth]{static/rounds_opponents_two_by_two_games_cooperation.pdf}
  \caption{\textbf{Cooperation rates over various social dilemmas for different
  limited memory payoffs.} ({\bf A}) If
  players update based on their last two rounds with another member of the population.
  ({\bf B}) If players update based on their last round with two other members of the population.
  ({\bf C}) If players update based on their last two rounds with two other members of the population.
  We vary the temptation
  payoff \(T \in \{0.2, 0.6, 1, 1.4, 1.8, 2.2\}\)
  across the \(x\) axis, and \(S \in \{1.2, 0.8, 0.4, 0, -0.4, -0.8\}\)
  across the \(y\) axis. Unless explicitly varied, the parameters of the simulation
  are $N\!=\!100$, $\beta\!=\!10$, $\delta\!=\!0.99$, $t\!=\!5\times 10^7$..}
  \label{fig:cooperation_rates_two_by_two_part_two}
\end{figure}

@@

\begin{algorithm}[!htbp]
  \SetAlgoLined
   $N \leftarrow$ population size\;
   $k \leftarrow 1$\;
   resident $\leftarrow (0, 0, 0)$\;
   \While{ $t <$ maximum number of steps}{
    mutant $\leftarrow$ random: $\{\emptyset \}\ \rightarrow R^3$\;
    fixation probability $\leftarrow \varphi $\;
    \If{$\varphi >$ random: $i \rightarrow [0, 1]$}{
      resident $\leftarrow$ mutant;
     }}
     \caption{Evolutionary process}\label{algorithm:pairwise_comparison}
\end{algorithm}

>>>>

%% Adding shortcut commands to refer to our figures %%
\newcommand{\FigEvoProc}{{\bf Fig.~1}} \newcommand{\FigInvAnalysis}{{\bfFig.~2}} \newcommand{\FigResultsOverPara}{{\bf Fig.~3}}

@@

\tikzset{treenode/.style = {align=center, inner sep=0pt, text centered,
  font=\sffamily}, arn_n/.style = {treenode, circle, white,
  font=\sffamily\bfseries, draw=black, inner sep=-6pt, fill=black, text
  width=1.5em},% arbre rouge noir, noeud noir
  arn_r/.style = {treenode, circle, red, text width=1.5em, very thick, inner
    sep=4pt},% arbre rouge noir, noeud rouge
  arn_x/.style = {treenode, rectangle, draw=black, minimum width=0.5em, minimum
    height=0.5em}% arbre rouge noir, nil
}

@@

\title{\bf  \sffamily \LARGE Evolution of cooperation among individuals with
limited payoff memory\\}
\date{}
\author{Nikoleta E. Glynatsi, Christian Hilbe, Alex McAvoy}

@@

\begin{abstract}
% Repeated games are vastly used in evolutionary game theory to explain
% cooperation in a variety of environments. Although existing models have shaped
% our understanding of human cooperation, they often work with idealized
% assumptions. In an evolutionary process, individuals imitate other individuals
% of the population based on their fitness. It is commonly assumed that an
% individual computes their fitness after interacting with a representative sample
% of the population, and remembering all the interactions they participated in. In
% real life, we do not always remember all our interactions, instead we rather
% recall our most recent ones.

% Here, we introduce a framework that allows individuals to estimate their fitness
% based on a minimum of social information. We explore the difference between our
% framework and the classical framework using computer simulations. We present
% results for the most commonly used classes of symmetric \(2 \times 2\) games.
% The simulations show that, in the prisoner's dilemma individuals with limited
% memory tend to adopt less generous strategies and they achieve less cooperation
% than in the classical scenario. In contrast, in the stag-hunt and the harmony
% game, the impact of memory is less striking. Here individuals with limited
% memory perform nearly as well as individuals with full memory. Finally, we
% observe that the snowdrift game is the only game for which cooperation can be
% underestimated in the classical scenario.
\end{abstract}

@@

Evolutionary game theory~\cite{smith1982evolution, hofbauer1998evolutionary,
nowak2004evolutionary, hauert2005game} describes the evolutionary dynamics of
populations consisting of different types of interacting individuals.
Traditional approaches assume that individuals meet each other at random in an
infinitely large well-mixed population. An example of such a approach in the the
replicator dynamics. It describes how the abundance of strategic types in a
population changes based on their fitness, identified with the payoff resulting
from the game~\cite{cressman2014replicator}. In this deterministic formulation,
individuals with higher fitness, such as defectors, increase in abundance.
Ultimately, the system reaches a stable fixed point in which the population may
consist either of a single type or of a mixture of different types.

It has been shown that the finiteness of populations may lead to fundamental
changes in this picture due to stochastic effects In this framework
disadvantageous mutants have a small, yet non-zero probability to reach fixation
in a finite population.

Its most prominent application is the quest for the origins and 
evolution of cooperation.
An important application of evolutionary game theory is the evolution of
cooperation which remains one of the greatest problems for biological and social
sciences.

% To explain the evolution of cooperation remains one of the greatest problems for
% biological and social sciences. Cooperation is the action of choosing to help
% others at one's own expense. The standard game of formulating such situation is
% the Prisoner's Dilemma~\cite{trivers1971evolution,
% milinski1987tit, glynatsi2021bibliometric, ohtsuki2006simple}, in which two
% players can choose to cooperate or to defect. The players are offered a certain
% payoff, \(R\), for mutual cooperation and a lower payoff, \(P\), for mutual
% defection. If one player cooperates while the other defects, then the cooperator
% gets the lowest payoff, \(S\), while the defector gains the highest payoff,
% \(T\). Thus, the payoffs have the following property \(T > R > P > S\), making
% defection the dominant strategy in the non-repeated game.

% In the repeated Prisoner's Dilemma, direct reciprocity can allow cooperators to
% not be exploited by defectors~\cite{axelrod1981evolution, nowak1992tit,
% nowak1992evolutionary}, however, how do such cooperators can evolve?

 , and 
in general, defectors are stable against invasion by cooperators.

In this framework disadvantageous mutants have a small, yet non-zero probability
to reach fixation in a finite population.

Two classes of microscopic processes have been used extensively: (i)
fitness-based processes in which an individual chosen proportional to fitness
reproduces and the offspring replaces a randomly chosen individual [11]; (ii)
pairwise comparison processes in which a pair of individuals is chosen, and
where subsequently one of these individuals may adopt the strategy of the other.

In the pairwise process considers a finite population of fixed size.In the
population at a time step different types of individuals can exist. 
Each individual can be of one of two types, A and B. The state of the population
is thus characterized by the number i of individuals of type A.

The interaction between the two types of individuals is described by the
functions $\pi _{{\rm A}}^{i}$ and $\pi _{{\rm B}}^{i}$. These indicate the
expected payoff for two types in a population in state i. The interaction can be
generated from a two-player matrix game which leads to payoffs linear in i [26],
but we keep the formalism general to include games played between an arbitrary
number of players, which leads to payoffs that depend on i in a polynomial way
[27–30]. In fact, our results hold for an arbitrary dependence of the payoffs on
i.

At each step an individual change their type based. This very cooperators
can repeas.

This model has several assumptions. Two assumptions are that initally it is
assumed that time to interact is faster than the time of the population
update. Secondly it is assumed that the indiviail can interact will every
other population member, and recall their interaction perfecttly.

The first assumption was questioned by the work of.

In this work

@@

In the following, we consider a well mixed population of fixed size. In each
step of t

We study the transmission of strategies with a frequency-dependent birth-death
process26 in a finite population of size n. In each time step, two randomly
chosen individuals compare their payoffs and one of them can switch to the other
one's strategy. This process can be interpreted as a model for social learning,
whereby successful strategies spread, and, occasionally, random strategy
exploration introduces novel strategies (corresponding to mutations in
biological models).

@@

To investigate the role of extortion in the context of evolutionary games, we
concentrate on the donation game

@@

\begin{figure}[!htbp]
    \centering
    \includegraphics[width=.70\textwidth]{static/expected_and_stochastic_for_donation_game.pdf}
    % \includegraphics[width=.70\textwidth]{static/expected_and_stochastic_for_donation_game_b_10.pdf}
    \caption{{\bf Evolutionary dynamics under expected payoffs and last round with one interaction payoffs.} 
    We have run two simulations of the evolutionary process described in
    section~\ref{section:model} for $t\!=\!10^7$ time steps. For each time step,
    we have recorded the current resident population ($y,p,q$). Since
    simulations are run for a relatively high continuation probability of
    $\delta\!=\!0.999$, we do not report the players' initial cooperation
    probability $y$. The graphs show how often the resident population chooses
    each combination ($p,q$) of conditional cooperation probabilities in the
    subsequent rounds. ({\bf A}) If players update based on their expected
    payoffs, the resident population typically applies a strategy for which
    $p\!\approx\!1$ and $q\!\le\!1\!-\!c/b\!=\!0.9$. ({\bf B}) When players
    update their strategies based on their realized payoffs in the last round,
    there are two different predominant behaviors. The resident population
    either consists of defectors (with $p\!\approx\!q\!\approx\!0$) or of
    conditional cooperators. In the latter case, the maximum level of $q$
    consistent with stable cooperation is somewhat smaller compared to the
    expected-payoff setting, $q\!<\!0.5$. The cooperation rate within the
    resident population (averaged over all games and over all time steps) is
    close to 100\%. Parameters: $N\!=\!100$, $c\!=\!1$, $\beta\!=\!1$,
    $\delta\!=\!0.999$.}
    \label{fig:expected_and_stochastic_for_donation}
\end{figure}

\begin{figure}[!htbp]
  \centering
  \includegraphics[width=.9\textwidth]{static/cooperation_rates_expected_and_stochastic_for_donation_game.pdf}
\end{figure}

@@

% \subsection{Effect of updating payoffs in different social
% dilemmas}\label{section:2_by_2_games}

% In the previous section we gained insights into the effects of the updating
% payoffs, and into how parameters such as the benefit and the strength of
% selection can intensify them. We investigated these effects by using the
% donation game. In order to broaden our understanding of the updating payoffs on
% different forms of possible human interactions we extend our approach to all \(2
% \times 2\) symmetric games. More specifically, we apply our analysis to four
% different classes of games; the harmony, the snowdrift, the prisoner's dilemma
% and the stag-hunt games.

% We compare the results of the evolutionary process when the updating payoffs are
% based on the expected payoffs, and on the last round payoffs for all the four
% possible classes of games (Figures~\ref{fig:expected_two_by_two}
% and~\ref{fig:last_round_two_by_two}). In Figure~\ref{fig:expected_two_by_two}
% each sub figure represents a run of evolutionary process for a different set of
% values for \(\mathcal{U}\). Without loss of generality we set \(R=1\) and
% \(P=0\)~\cite{Martinez2012, Roca2009}, and we vary the values of the temptation
% payoff \(T\) (across the \(x\)-axis) and of the sucker's payoff \(S\) (across
% the \(y\)-axis). Starting at the upper left corner and proceeding clockwise the
% quadrants correspond to the harmony, the snowdrift, the prisoner's dilemma and
% the stag-hunt games.

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[width=\textwidth]{static/expected_two_by_two_games.pdf}
%   \caption{{\bf Evolutionary dynamics under expected payoffs for various social dilemmas.}
%   We vary the temptation payoff \(T \in \{0.2, 0.6, 1, 1.4, 1.8, 2.2\}\) across
%   the \(x\) axis, and  \(S \in \{1.2, 0.8, 0.4, 0, -0.4, -0.8\}\) across the
%   \(y\) axis. ({\bf A}) The top left quadrant where \(S > 0\) and \(T \leq 1\)
%   corresponds to the harmony game. The preference ordering for the harmony game
%   is \(R > T > S > P\). ({\bf B}) The top right quadrant where \(S > 0\) and \(T
%   > 1\) corresponds to the snowdrift game. The preference ordering for the
%   snowdrift game is \(T > R > S > P\). ({\bf C}) The bottom left quadrant where
%   \(S < 0\) and \(T \leq 1\) corresponds to the stag-hunt game. The preference
%   ordering for the stag-hunt game is \(R > T > P > S\). ({\bf D}) The bottom
%   right quadrant where \(S < 0\) and \(T > 1\) corresponds to the prisoner's
%   dilemma game. The preference ordering for the prisoner's dilemma game is \(T >
%   R > P > S\). Unless explicitly varied, the parameters of the simulation are
%   $N\!=\!100$, $\beta\!=\!10$, $\delta\!=\!0.99$, $t\!=\!5\times 10^7$.}
%   \label{fig:expected_two_by_two}
% \end{figure}

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[width=\textwidth]{static/stochastic_two_by_two_games.pdf}
%   \caption{{\bf Evolutionary dynamics under last round payoffs for various social dilemmas.} 
%   We vary the temptation payoff \(T \in \{0.2, 0.6, 1, 1.4, 1.8, 2.2\}\) across
%   the \(x\) axis, and  \(S \in \{1.2, 0.8, 0.4, 0, -0.4, -0.8\}\) across the
%   \(y\) axis. ({\bf A}) The top left quadrant where \(S > 0\) and \(T \leq 1\)
%   corresponds to the harmony game. The preference ordering for the harmony game
%   is \(R > T > S > P\). ({\bf B}) The top right quadrant where \(S > 0\) and \(T
%   > 1\) corresponds to the snowdrift game. The preference ordering for the
%   snowdrift game is \(T > R > S > P\). ({\bf C}) The bottom left quadrant where
%   \(S < 0\) and \(T \leq 1\) corresponds to the stag-hunt game. The preference
%   ordering for the stag-hunt game is \(R > T > P > S\). ({\bf D}) The bottom
%   right quadrant where \(S < 0\) and \(T > 1\) corresponds to the prisoner's
%   dilemma game. The preference ordering for the prisoner's dilemma game is \(T >
%   R > P > S\). Unless explicitly varied, the parameters of the simulation are
%   $N\!=\!100$, $\beta\!=\!10$, $\delta\!=\!0.99$, $t\!=\!5\times 10^7$.}
%   \label{fig:last_round_two_by_two}
% \end{figure}

% The harmony game describes an interaction without conflict. In the harmony game
% it is in the best interest for both players to cooperate, and in an evolutionary
% process cooperators prevail. We observe that for most harmony game runs the
% resident population overwhelmingly applies a strategy for which \(p\) and \(q\)
% are \(\approx 1\) (Figure~\ref{fig:expected_two_by_two}). The snowdrift game
% describes a situation similar to that of the prisoner's dilemma; cooperation
% results in a benefit to the opposing player but entailing a cost to the
% cooperator. However, in the snowdrift game individuals obtain immediate direct
% benefits from the cooperative acts which leads to \(S > P\). In the snowdrift
% game more cooperation emerges compared to the prisoner's dilemma. Defection is
% never a resident strategy and for the same values of temptation the overall
% \(q-\) values are higher. The last class of games we present are for the
% stag-hunt game. In the stag-hunt game there is an equilibrium in which both
% players cooperate as well as one in which both defect. For small values of the
% temptation and the sucker's payoffs we observe that cooperation prevails similar
% to the harmony game. However, in the case where the temptation and the reward
% payoffs are equal the resident population either consists of defectors or
% cooperators.

% Although the patterns of the evolved populations remain similar if we consider
% that players update their strategies based on their last round payoff
% (Figure~\ref{fig:last_round_two_by_two}), there are still dissimilarities
% between the two approaches. To better understand these dissimilarities, we
% explore the cooperation rates for each of the cases of the social dilemmas we
% have presented (Figure~\ref{fig:cooperation_rates_two_by_two_part_one}).

% In the harmony game the cooperation rates for both approaches are similar. The
% biggest difference occurs for \(T=1\), nevertheless, it is less than 10\%. There
% are two instances for which the cooperation rates are higher for the limited
% memory payoffs compared to the expected. These are for \(T=2.2, S=0.4\) and for
% \(T=2.2, S=0.8\). It is only in the snowdrift game that cooperation is
% overestimated when a minimum of information is considered. Players are slightly
% more likely to cooperate after a cooperation and to forgive after being at the
% receiving end of a defection. For the rest of the cases the classical scenario
% overestimates the average cooperation rate, supporting the results of the
% previous section. There is a substantial difference in the cooperation rates for
% the prisoner's dilemma class. We observe that for \(S<-0.4\) cooperation almost
% never emerges if players imitate based only on the last round payoff.

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[width=.4\textwidth]{static/expected_two_by_two_games_cooperation.pdf}
%   \includegraphics[width=.4\textwidth]{static/stochastic_two_by_two_games_cooperation.pdf}
%   \caption{\textbf{Cooperation rates for various social dilemmas.} ({\bf A}) If
%   players update based on their expected payoffs. ({\bf B}) If players update
%   based on their last round payoffs. We vary the temptation payoff \(T \in
%   \{0.2, 0.6, 1, 1.4, 1.8, 2.2\}\) across the \(x\) axis, and \(S \in \{1.2,
%   0.8, 0.4, 0, -0.4, -0.8\}\) across the \(y\) axis. Unless explicitly varied,
%   the parameters of the simulation are $N\!=\!100$, $\beta\!=\!10$,
%   $\delta\!=\!0.99$, $t\!=\!5\times
%   10^7$.}\label{fig:cooperation_rates_two_by_two_part_one}
% \end{figure}

% So far we have explored the difference between the expected payoffs and the last
% round payoffs. In order to explore further the effect of limited memory we allow
% individuals to remember more. More precisely, up to two interactions and up to
% the last two rounds. In total we present results for three more updating
% payoffs. These are the payoffs when individuals consider the last two rounds
% with another member of the population, the last round with two members of the
% population, and the last two rounds with two members of the population. Similar
% to the last round payoff, we use simulations and record which strategies the
% players adopt over time based
% (Appendix~\ref{appendix:further_simulation_results}) and we compare the evolving
% cooperation rates to those of the expected payoffs
% (Figure~\ref{fig:cooperation_rates_two_by_two_part_two}).

% In the case of the last two rounds payoff we make two observations. Initially,
% for the harmony, the stag-hunt and the prisoner's dilemma classes the average
% cooperation rates are higher than the previous case of the last round payoff.
% The rates remain strictly less than in the expected payoffs, however, in the
% case of the prisoner's dilemma we observe a significant increase. Secondly, for
% the snowdrift class there are more instances for which the cooperation rates are
% higher than in the expected payoffs. This could indicate that in the case of the
% snowdrift game the expected payoffs underestimate cooperation. Once players
% interact with two other members of the population, instead of one, the expected
% payoffs strictly yield a higher cooperation rate  even in the case of the
% snowdrift game. Similar to the previous result, the difference between the two
% approaches is always higher for the prisoner's dilemma class.

% \begin{figure}[!htbp]
%   \centering
%   \includegraphics[width=.33\textwidth]{static/rounds_two_by_two_games_cooperation.pdf}
%   \includegraphics[width=.33\textwidth]{static/opponents_two_by_two_games_cooperation.pdf}
%   \includegraphics[width=.33\textwidth]{static/rounds_opponents_two_by_two_games_cooperation.pdf}
%   \caption{\textbf{Cooperation rates over various social dilemmas for different
%   limited memory payoffs.} ({\bf A}) If players update based on their last two
%   rounds with another member of the population. ({\bf B}) If players update
%   based on their last round with two other members of the population. ({\bf C})
%   If players update based on their last two rounds with two other members of the
%   population. We vary the temptation payoff \(T \in \{0.2, 0.6, 1, 1.4, 1.8,
%   2.2\}\) across the \(x\) axis, and \(S \in \{1.2, 0.8, 0.4, 0, -0.4, -0.8\}\)
%   across the \(y\) axis. Unless explicitly varied, the parameters of the
%   simulation are $N\!=\!100$, $\beta\!=\!10$, $\delta\!=\!0.99$, $t\!=\!5\times
%   10^7$..}
%   \label{fig:cooperation_rates_two_by_two_part_two}
% \end{figure}

@@

\begin{algorithm}[!htbp]
  \SetAlgoLined $N \leftarrow$ population size\; $k \leftarrow 1$\; resident
   $\leftarrow (0, 0, 0)$\; \While{ $t <$ maximum number of steps}{mutant
   $\leftarrow$ random: $\{\emptyset \}\ \rightarrow R^3$\; fixation probability
   $\leftarrow \varphi $\; \If{$\varphi >$ random: $i \rightarrow [0,
   1]$}{resident $\leftarrow$ mutant;}} \caption{Evolutionary
   process}\label{algorithm:pairwise_comparison}
\end{algorithm}
